### 2014-02-23 paper/retrofit.tex
Split ifc figure into two parts.
TSNI theorem.

ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
\end{code}

\begin{mathpar}
\inferrule[I-evalCtx]
{|
iconf iS (tconf id il ie)
.->
iconf iS' (tconf id il' ie')
|}
{|
iconf iS (lconf id il tS (iniE ie), ldots)
.->
iS' ; sched step (lconf id il' tS (iniE ie'), ldots)
|}

@@

\and
\inferrule[T-border]
{ } {| conf tS (intE (TI (IT (te)))) -> conf tS (intE te)|}
\end{mathpar}
\caption{IFC language nad general embedding.}
\label{fig:ml}
\end{figure}

@@

>>>>

ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
\end{code}
\caption{IFC grammar.}
\label{fig:ifc-grammar}
\end{figure}

\begin{figure}
\begin{mathpar}
\inferrule[I-evalCtx]
{|
iconf iS (tconf id il ie)
.->
iconf iS' (tconf id il' ie')
|}
{|
iconf iS (lconf id il tS (iniE ie), ldots)
.->
iS' ; sched step (lconf id il' tS (iniE ie'), ldots)
|}

@@

\and
\inferrule[T-border]
{ } {| conf tS (intE (TI (IT (te)))) -> conf tS (intE te)|}
\end{mathpar}
\caption{IFC language and general embedding.}
\label{fig:ifc}
\end{figure}

@@

\subsection{Formal Guarantees}

\begin{theorem}[Termination Sensitive Non-Interference (TSNI)]
  For any two list of tasks |its1|, |its2|, |its2|, label |il|,
  IFC states |iS1|, |iS2|, |iS1'|, where
  \[
    |its1| \approx_{|il|} |its2| \qquad \text{and} \qquad
    |iconf iS1 its1| |.->|^* |iconf iS1' its1'|
  \]
  then there exists a list of tasks |ts2'| and an IFC state |iS2'| such that
  \[
    |iconf iS2 its2| |.->|^* |iconf iS2' its2'| \qquad \text{and} \qquad
    |its1'| \approx_{|il|} |its2'|
    \ \text{.}
  \]
\end{theorem}
